Ecuador plant species list

### 2022-08-23 code/L0/L0_1_Ecuador_plant_species_lists.Rmd
add code for POWO and GBIF files

---
title: "Ecuador plant species list"
authors: "Hazel Anderson"
collaborators: "None"
data input: "None"
data output: "Ecuador_plant_species_list.csv"
project: "Frugivoria"
date: "2022-08-17"
output: html_document
---
# Set Working directory & file path
```{r}
setwd()
data_path <- 'G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0'
```

# Load required packages
```{r}
library(BIEN)
library(kewr)
library(gbifdb)
```

# Pull data from various sources

## BIEN
```{r}
Ecuador <- BIEN_occurrence_country("Ecuador")
```

## Kew
```{r}

```

## GBIF
```{r}

```

>>>>

---
title: "Ecuador plant species list"
authors: "Hazel Anderson"
collaborators: "None"
data input: "None"
data output: "Ecuador_plant_species_list.csv"
project: "Frugivoria"
date: "2022-08-17"
output: html_document
---
# Set Working directory & file path
```{r}
#setwd() *WHAT SHOULD THIS BE???
data_path <- 'G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0'
```

# Load required packages
```{r}
library(BIEN)
```

# Pull Ecuador plant species lists from various sources

## BIEN
```{r}
Ecuador_BIEN <- BIEN_occurrence_country("Ecuador")
write.csv(Ecuador_BIEN, "Ecuador_BIEN_species_list.csv")
```

## Kew Plants of the World Online
```{r}
library(readxl)
Ecuador_POWO <- read_excel("G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0/PlantsOfTheWorldOnline_Ecuador_species.xlsx")
```

## GBIF
```{r}
Ecuador_GBIF <- read.csv("G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0/GBIF_Ecuador_PlantSpeciesList.csv")
```
